Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-29 tex/ClementiBarba2020.tex
attempt to acknowledgment

>>>>

\section{Acknowledgments}

We thank Dr. Chase T. Ellis  and Dr. Joseph G. Tischler for the fruitful discussion regarding the result of their paper \cite{ellis2016}, 
what lead to the validation of \pygbe. We would like to thank them also for providing a mesh file and dielectric data that made the modeling closer to their original setup.
Last but not least we would like to thank Dr. Christopher D. Cooper for the valuable discussions that help to overcome some of the challenges presented through out the 
generation of the results.
